---
title: "Reproducible Research: Peer Assessment 1"
author: "wen"
date: "2021/12/20"
output: html_document
---
##1.Loading and preprocessing the data
```{r,echo = TRUE}
dataset1<-read.csv("activity.csv")
show(dataset1)

```
##2.What is mean total number of steps taken per day?
###2(1).Calculate the total number of steps taken per day
```{r,echo = TRUE}
stepsperday <- aggregate(steps~date, dataset1, sum)
show(stepsperday)
```
###2(2). the histogram of the total number of steps taken each day
```{r,echo = TRUE}
hist(stepsperday$steps,xlab = "Steps")
```
###2(3). Calculate and report the mean and median of the total number of steps taken per day
```{r,echo = TRUE}
mean_num <- mean(stepsperday$steps)
mean_num
median_num <- median(stepsperday$steps)
median_num
```
##3.What is the average daily activity pattern?
###3(1).Subset the original data to calculate the average number of steps taken of the 5-minute interval
```{r,echo = TRUE}
average_num <- aggregate(steps~interval, dataset1, mean)
show(average_num)
```
###3(1).Make a time series plot (i.e. \color{red}{\verb|type = "l"|}type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r,echo = TRUE}
with(average_num , plot(interval, stepstype="l"))
```
###3(2). Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
The interval contains maximum:
```{r,echo = TRUE}
maximum <- max(average_num$steps)
interval<- subset(average_num, steps==maximum)
interval
```
##4.Imputing missing values
###4(1).Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)
```{r,echo = TRUE}
colSums(is.na(dataset1))
```
###4(2).use column "newsteps" contains the average steps in each interval
```{r,echo = TRUE}
dataset1$newsteps <- average_num$steps
show(dataset1)
```
###4(3).fill the data
```{r,echo = TRUE}
dataset1$steps[is.na(dataset1$steps)] <- dataset1$newsteps
show(dataset1)
```
###4(4)
```{r,echo = TRUE}
dataset1$newsteps <- NULL
dataset2 <- dataset1
show(dataset2)
sum1<- aggregate(steps~date,dataset2, sum)
show(sum1)
hist(dataset2$steps,xlab = "Steps")
mean_num2 <- mean(dataset2$steps)
mean_num2
median_num2 <- median(dataset2$steps)
median_num2
```
###the differences of the mean and median between the first and second part
```{r,echo = TRUE}
mean_num2-mean_num
median_num2-median_num
```
##5.Are there differences in activity patterns between weekdays and weekends?
###5(1).Create a new factor variable in the dataset with two levels – “weekday” and “weekend” indicating whether a given date is a weekday or weekend day.
###after installed timedate pack
```{r,echo=TRUE}
library(timeDate)
dataset2$Weekday <- isWeekday(dataset2$date)
show(dataset2)
```
###add Weekday & weeekend
```{r,echo = TRUE}
weekday <- subset(dataset2, dataset2$Weekday == "TRUE")
mean_weekday <- aggregate(steps ~ interval, data = weekday, mean)
show(mean_weekday)
weekend <- subset(dataset2, dataset2$Weekday == "FALSE")
mean_weekend <- aggregate(steps ~ interval, data = weekend, mean)
show(mean_weekend)
```
###5(2).Make a panel plot containing a time series plot (i.e. \color{red}{\verb|type = "l"|}type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis). See the README file in the GitHub repository to see an example of what this plot should look like using simulated data.
```{r,echo = TRUE}
layout(matrix(c(1,1,2,2), 2, 2, byrow = TRUE))
plot(mean_weekday$interval, mean_weekday$steps, xlab = "interval", ylab = "Number of steps", main ="Weekday") 
plot(mean_weekend$interval, mean_weekend$steps, xlab = "interval", ylab = "Number of steps", main ="Weekend")
```
